\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT}

\begin{center}
    \textbf{Implementation and Integration of a Web-Based Monitoring Dashboard Frontend for Water Treatment Plant Dosing Automation} \\
    \vspace{0.4cm}
    by \\
    \vspace{0.4cm}
    Matthew Nicholas Gunawan\\
    18222058\\
\end{center}

\begin{spacing}{1.0}
A Water Treatment Plant (WTP) requires water quality monitoring and chemical
dosing processes so that operators can recognize changes in conditions
accurately. Monitoring that relies on separate instruments and records makes it
difficult for operators to observe pH, turbidity, and Total Dissolved Solids
(TDS) parameters, as well as the condition of chemicals and dosing pumps. This
final project focuses on the implementation and integration of a web-based
dashboard frontend for the dosing automation system of the ITB Jatinangor WTP.

The frontend is developed using Next.js, React, and TypeScript, and is
integrated with the backend through a REST API. The dashboard is designed to
provide operator authentication, a compliance summary with respect to the
Regulation of the Minister of Health (Permenkes), sensor data visualization,
data history and export, alarm monitoring, pump status, dose offset
configuration, and stale data warnings. TanStack Query is used to manage server
data, while Progressive Web App support allows the application to be installed
and used on both desktop and mobile devices. The scope of this final project is
limited to the frontend implementation, while the sensor devices, backend,
database, and dose control algorithm are outside the scope.

The evaluation is carried out through functional testing of the main frontend
requirements and flows. The test results show that all 20 functional test cases
were successfully fulfilled. These results verify that the frontend is able to
handle authentication, display monitoring summaries and sensor analytics,
export data history, and validate alarm and dose offset interactions in
accordance with the system requirements.

\noindent\textbf{Keywords:} dashboard, frontend, water treatment plant, Next.js, Progressive Web App.
\end{spacing}
